### 2022-11-16 project_Antonio/paper.tex
fix title

\def\Student{Antonio Paredes Sotelo}
\def\Title{Anteproyecto}
\def\Prog{Doctorado en Ciencias (F\'{i}sica) }
\def\Dept{Departamento de Investigac\'{i}on en Fis\'{i}ca}
\def\Director{Dr. Jos\'{e} Feliciano BEN\'{I}TEZ RUBIO}
\def\ProjectTitle{B\'usqueda de part\'iculas de Higgs con modelos de f\'sica m\'as all\'a del Modelo Est\'andar y medici\'on de la luminosidad usando el m\'etodo de Pixel Cluster Counting en el experimento CMS del CERN}
\def\ProjectTitleEnglish{Search for Higgs bosons using models of physics beyond the Standard Model and measurement of luminosity using the Pixel Cluster Counting method in the CMS experiment at CERN}
\def\ResearchLine{F\'{i}sica Matematicas}

>>>>

\def\Student{Antonio Paredes Sotelo}
\def\Title{Anteproyecto}
\def\Prog{Doctorado en Ciencias (F\'{i}sica) }
\def\Dept{Departamento de Investigac\'{i}on en Fis\'{i}ca}
\def\Director{Dr. Jos\'{e} Feliciano BEN\'{I}TEZ RUBIO}
\def\ProjectTitle{B\'usqueda de part\'iculas de Higgs con modelos de f\'isica m\'as all\'a del Modelo Est\'andar y medici\'on de la luminosidad usando el m\'etodo de Pixel Cluster Counting en el experimento CMS del CERN}
\def\ProjectTitleEnglish{Search for Higgs bosons using models of physics beyond the Standard Model and measurement of luminosity using the Pixel Cluster Counting method in the CMS experiment at CERN}
\def\ResearchLine{F\'{i}sica Matematica}
